---
title: "Abacavirinol"
author: "Natalie Gavia"
date: "December 5, 2018"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
abac <-read.csv(file="abacavirinol.csv",header=TRUE)
Female <- filter(abac,sex=="F")
Male  <- filter(abac,sex=="M")
Druggies <- filter(abac,Ivdrug=="M")
DruggiesUse <- filter(abac,Ivdrug== "user")
LBGT <- filter(abac,LBGT=="yes")
```

# Introduction 

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. Finish this! ADD B

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!--> 
For each variable, we will make seperate data results for Graphical, Numerical, and Inferential results. The methods that we'll be using for each one would be barchartGC, colPerc and rowPerc, chisqtestGC and fisher.test.

```{r}
lbgtGrp <- filter(abac, LBGT == "yes")
```

```{r}
sexgrp <- filter(abac, sex == "F")
```


```{r}
sexgrp <- filter(abac, sex == "M")
```

```{r}
infectedgrp <- filter(abac, infected == "aids")
```

```{r}
infectedgrp <- filter(abac, infected == "none")
```

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

The results are categorized into three sections; Graphical, NUmerical, and Inferential results.

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->


Every Participant
```{r}
results <- xtabs(~infected+treatment, data=abac)
barchartGC(results, type ==  "percent")

```
The graph above displays every participant that took the drug and the placebo. From the data, it appears that those that took the placebo had a higher chance of contracting the virus that those that took the drug. This indicates that the drug is actually working since those that took the drug had a lesser chance of contracting the virus.



Female
```{r}
femaleresults <- xtabs(~infected+treatment, data=Female)
barchartGC(femaleresults, type ==  "percent")

```

The graph above shows women taking the placebo and the drug. As seen in the graph, it appears that those that took the  drug contracted aids than those that took the placebo.However, it shows it was only a slight difference.


Male
```{r}
maleresults <- xtabs(~infected+treatment, data=Male)
barchartGC(maleresults, type ==  "percent")

```

The graph above shows males taking the drug and the placebo. Those that took the placebo had a higher risk factor of getting infected with aids comapred to those that took the drug.

LGBT Graph

```{r}
lbgtresults <- xtabs(~infected+treatment, data=LBGT)
barchartGC(lbgtresults, type ==  "percent")

```
The graph above shows the LGBT community taking the drug and placebo. In this group, it appears that those that took the drug ended up having higher chances of contracting aids than those that took the placebo. This data results is odd since other variables, such as gende and drug users justifies that the drug is working. There must be some outside factor affecting this group.



Druggies
```{r}
druggiesusersresults <- xtabs(~infected+treatment, data= DruggiesUse)
barchartGC(druggiesusersresults, type ==  "percent")

```
In the first bar graph, those that got aids were those that took the placebo. While those that took the drug, did not contract AIDS. This possibly indicates that the drug is working.






### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

Every Participant
```{r}
colPerc(results)
rowPerc(results)
```

From the data above, it shows that those had the placebo has a higher change of contracting aids. Since The placebo group had a 1.5% high. Potentally making the effects of the real drug working.

Female and Male
```{r}
colPerc(femaleresults)
rowPerc(femaleresults)
```
From the colPerc data, it appears that females that took the drug had a 1.1 percent of getting aids than those that took the placebo.

```{r}
colPerc(maleresults)
rowPerc(maleresults)
```
In the data results for males, it shows that those that took the placebo had a 4.78 percent chance of getting aids than those that took the medication. Justifiying that the drug works effectively for males.

Drug Users

```{r}
colPerc(druggiesusersresults)
rowPerc(druggiesusersresults)
```

The colPerc above shows Drug users thathad the placebo had a 4.23 percent chance higher of getting aids than those that took the drug. This can suggest that the drug is efective for this ggroup of vairables. 


LBGT 

```{r}
colPerc(lbgtresults)
rowPerc(lbgtresults)
```
In the colPerc above, it appears that those that took the drug had a 3.45 percent chance of contracting aids than those that took the placebo.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

Every Participant


```{r}
chisqtestGC(results, graph = TRUE)
```
```{r}
fisher.test(results)
```



The null hypothesis is rejcted since the P value is low. This means that the drug is working, backed up by the P value only being 0.01634.
From the Fricher test, it seems that by taking the drug, you have a less likely chance of getting aids. This is justified by the Drugs odds ratio, which is 0.7181794

Female and Male

```{r}
chisqtestGC(femaleresults, graph = TRUE)
```
```{r}
fisher.test(femaleresults)
```

We reject the null hypothesis since the p value is 0.04911 ( below 0.05)

Male

```{r}
chisqtestGC(maleresults, graph = TRUE)
```
```{r}
fisher.test(maleresults)
```

We would reject the null hypothesis since the p-value was below 0.05. Specifically it was 0.000004352.


DrugUsers

```{r}
chisqtestGC(druggiesusersresults, graph = TRUE)
```
```{r}
fisher.test(druggiesusersresults)
```
We reject the null hypothesis here since the p-value was 0.01929, which is below 0.05.


LBGT
```{r}
chisqtestGC(lbgtresults, graph = TRUE)
```

```{r}
fisher.test(lbgtresults)
```

We accept the null hypothesis here since the p-value was 0.05698.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Two out of the four variables, explayed excellent results of the drug working. Those groups were the Drug users and Males, both demonstrating an overall effectiveness of the medication by having a lesser chance of contracting aids. The other variables, Females and the LGBT community had the opposite effect for them. Throughout each dataset, it appears that the medication did not work out as well as the Drug users/Males. But rather increased the proability of getting aids. There must be some outside factor that influences both Females and the LGBT community of getting aids through the medication. 

